Synthetic data

### 2022-04-29 dev/submissions/aies/extended_abstract/extended_abstract.tex
adapted code to changes to CounterfactualExplanations package. Still need to rerun remaining experiments, for now just ran POC for AIES.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  sigconf]{acmart}
\usepackage{amsmath}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Dynamics in Algorithmic Recourse},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

% \ConferenceShortName{AIES '22}
% \ConferenceName{Fifth AAAI/ACM Conference on Artificial Intelligence, Ethics, and Society}

@@

\author{Patrick Altmeyer}
\affiliation{%
  \institution{Delft University of Technology}
  \city{Delft}
  \country{The Netherlands}
}
\email{p.altmeyer@tudelft.nl}
\orcid{0000-0003-4726-8613}
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Dynamics in Algorithmic Recourse}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Trustworthy Artificial Intelligence for Finance and Economics}
\author{}
\date{April 26, 2022}

@@

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics[width=\textwidth,height=1.04167in]{.pdf}

@@

\caption{\label{fig-dynamics}PLACEHOLDER: The dynamics of algorithmic
recourse.}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  sigconf]{acmart}
\usepackage{amsmath}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Dynamics in Algorithmic Recourse},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
% \ConferenceShortName{AIES '22}
% \ConferenceName{Fifth AAAI/ACM Conference on Artificial Intelligence, Ethics, and Society}

@@

\author{Patrick Altmeyer}
\affiliation{%
  \institution{Delft University of Technology}
  \city{Delft}
  \country{The Netherlands}
}
\email{p.altmeyer@tudelft.nl}
\orcid{0000-0003-4726-8613}
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\renewcommand*\contentsname{Table of contents}
\renewcommand*\listfigurename{List of Figures}
\renewcommand*\listtablename{List of Tables}
\renewcommand*\figurename{Figure}
\renewcommand*\tablename{Table}
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Dynamics in Algorithmic Recourse}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Trustworthy Artificial Intelligence for Finance and Economics}
\author{}
\date{today}

@@

@@

{\centering \includegraphics[width=0.45\textwidth,height=\textheight]{www/poc.png}

@@

\caption{\label{fig-dynamics}Dynamics in Algorithmic Recourse.}

### 2022-04-29 dev/work/synthetic_endogenous_shifts.qmd
adapted code to changes to CounterfactualExplanations package. Still need to rerun remaining experiments, for now just ran POC for AIES.

```{julia}
# Number of points to generate.
N = 100
using CounterfactualExplanations.Data
xs, ys = Data.toy_data_linear(N)
X = hcat(xs...) # bring into tabular format
data = zip(xs,ys)
```

@@

```{julia}
nn = Chain(Dense(2,1))
λ = 0.5
sqnorm(x) = sum(abs2, x)
weight_regularization(λ=λ) = 1/2 * λ^2 * sum(sqnorm, Flux.params(nn))
loss(x, y) = Flux.Losses.logitbinarycrossentropy(nn(x), y) + weight_regularization();
```

```{julia}
using Flux.Optimise: update!, ADAM
opt = ADAM()
epochs = 50
function _forward_nn(nn, data, epochs)
    for epoch = 1:epochs
        for d in data
            gs = gradient(params(nn)) do
            l = loss(d...)
            end
            update!(opt, params(nn), gs)
        end
    end
    return nn
end
_forward_nn(nn, data, epochs)
```

@@

```{julia}
#| echo: false
# Plot the posterior distribution with a contour plot.
plt = plot_contour(X',ys,M);
savefig(plt, joinpath(www_path, "nn_contour.png"))
```

@@

```{julia}
la = Laplace(nn, λ=λ)
BayesLaplace.fit!(la, data)
```

@@

```{julia}
#| echo: false
# Plot the posterior distribution with a contour plot.
plt = plot_contour(X',ys,Mᴸ);
savefig(plt, joinpath(www_path, "la_contour.png"))
```

@@

## Experiment

```{julia}
# Models:
models = (Bayesian=Mᴸ, Plugin=M)

# Generators:
generators = (Bayesian=GreedyGenerator(), Plugin=GenericGenerator())

# Variables:
μ = [0.01,0.1,0.25]
γ = [0.50,0.75,0.9]
grid_ = Experiments.GridVariables(μ, γ)
n_rounds = 10
n_folds = 5
target = 1.0
T = 1000
```

```{julia}
# Experiments:
experiment = Experiments.Experiment(X,ys,models[:Bayesian],target,grid_,n_rounds)
experiment_plugin = Experiments.Experiment(X,ys,models[:Plugin],target,grid_,n_rounds)
experiments = (experiment, experiment_plugin)
```

@@

```{julia}
#| eval: false
using Main.Experiments: plot_path
paths = [Experiments.load_path(joinpath(output_path, string(keys(generators)[j]))) for j ∈ 1:length(generators)];
anim = Experiments.plot_path(paths[1],Γ=γ,𝙈=μ)
gif(anim,joinpath(www_path,"bayesian.gif"), fps=2)
anim = Experiments.plot_path(paths[2],Γ=γ,𝙈=μ)
gif(anim,joinpath(www_path,"plugin.gif"), fps=2)
```

@@

  while epoch <= epochs && !stopping_criterium_reached
    for d in data
      gs = gradient(Flux.params(nn)) do
        l = loss(d...)
      end
      update!(opt, Flux.params(nn), gs)
    end
    avg_l = vcat(avg_l,avg_loss(data))
    plot!(p1, [0:epoch], avg_l, color=1)
    scatter!(p1, [0:epoch], avg_l, color=1)
    acc = vcat(acc,accuracy(data))
    plot!(p2, [0:epoch], acc, color=1)
    scatter!(p2, [0:epoch], acc, color=1)
    plt=plot(p1,p2, size=(600,300))
    frame(anim, plt)

@@

```{julia}
# Experiments:
experiment = Experiments.Experiment(X',y',models[:Bayesian],target,grid_,n_rounds)
experiment_plugin = Experiments.Experiment(X',y',models[:Plugin],target,grid_,n_rounds)
experiments = (experiment, experiment_plugin);
```

>>>>

```{julia}
Random.seed!(123)
using MLJ
N = 1000
X, ys = make_blobs(N, 2; centers=2, as_table=false, center_box=(-2 => 2), cluster_std=0.1)
ys .= ys.==2
X = X'
xs = Flux.unstack(X,2)
data = zip(xs,ys)
plt = plot()
plot_data!(plt,X',ys)
```

@@

```{julia}
nn = Chain(Dense(2,1))
loss(x, y) = Flux.Losses.logitbinarycrossentropy(nn(x), y) 
```

```{julia}
using Flux.Optimise: update!, ADAM
opt = ADAM()
epochs = 10
function _forward_nn(nn, data, epochs)
    for epoch = 1:epochs
        for d in data
            gs = gradient(Flux.params(nn)) do
            l = loss(d...)
            end
            update!(opt, Flux.params(nn), gs)
        end
    end
    return nn
end
_forward_nn(nn, data, epochs)
```

@@

```{julia}
#| echo: false
# Plot the posterior distribution with a contour plot.
plt_nn = plot_contour(X',ys,M;zoom=0);
savefig(plt_nn, joinpath(www_path, "nn_contour.png"))
```

@@

```{julia}
λ = 0.1
la = Laplace(nn, λ=λ)
BayesLaplace.fit!(la, data)
```

@@

```{julia}
#| echo: false
# Plot the posterior distribution with a contour plot.
plt = plot_contour(X',ys,Mᴸ;zoom=0)
savefig(plt, joinpath(www_path, "la_contour.png"))
```

@@

## Single Round

```{julia}
# Models:
models = (Bayesian=Mᴸ, Plugin=M)
# Generators:
generators = (Bayesian=GreedyGenerator(), Plugin=GenericGenerator(ϵ=0.01))
```

### Generate counterfactual

```{julia}
cb = false
γ = 0.75
mod = Mᴸ
gen = generators[:Plugin]
plt_original = plt_nn = plot_contour(X',ys,mod;zoom=0,colorbar=cb,title="(a)")
```

```{julia}
counterfactual_data = CounterfactualData(X,ys')
μ = 0.10
Random.seed!(123)
candidates = findall(ys.==0)
chosen = rand(candidates, Int(round(μ*length(candidates))))
X′ = copy(X)
y′ = copy(ys)
using CounterfactualExplanations.Counterfactuals: counterfactual, counterfactual_label
for i in chosen
    x = X[:,i]
    outcome = generate_counterfactual(x, 1, counterfactual_data, mod, gen,γ=γ)
    X′[:,i] = counterfactual(outcome)
    y′[i] = counterfactual_label(outcome)
end
plt_single = plot_contour(X′',y′,mod;zoom=0,colorbar=cb,title="(b)")
```

### Retrain

```{julia}
xs′ = Flux.unstack(X′,2)
data = zip(xs′,y′)
mod = retrain(mod, data)
plt_single_retrained = plot_contour(X′',y′,mod;zoom=0,colorbar=cb,title="(c)")
```

### Repeat

```{julia}
i = 2
while i <= 10
    counterfactual_data = CounterfactualData(X′,y′')
    Random.seed!(123)
    candidates = findall(y′.==0)
    chosen = rand(candidates, Int(round(μ*length(candidates))))
    xs′ = Flux.unstack(X′,2)
    data = zip(xs′,y′)
    mod = retrain(mod, data)
    for i in chosen
        x = X′[:,i]
        outcome = generate_counterfactual(x, 1, counterfactual_data, mod, gen; γ=γ)
        X′[:,i] = counterfactual(outcome)
        y′[i] = counterfactual_label(outcome)
    end
    i += 1
end
plt_single_repeat = plot_contour(X′',y′,mod;zoom=0,colorbar=cb,title="(d)")
```

```{julia}
plt = plot(plt_original, plt_single, plt_single_retrained, plt_single_repeat, layout=(1,4), legend=false, axis=nothing, size=(600,165))
savefig(plt, joinpath(www_path, "poc.png"))
```

## Experiments

```{julia}
# Variables:
μ = [0.05,0.1,0.25]
γ = [0.50,0.75,0.9]
grid_ = Experiments.GridVariables(μ, γ)
n_rounds = 10
n_folds = 5
target = 1.0
T = 1000
```

```{julia}
# Experiments:
experiment = Experiments.Experiment(X,ys,models[:Plugin],target,grid_,n_rounds)
experiment_plugin = Experiments.Experiment(X,ys,models[:Plugin],target,grid_,n_rounds)
experiments = (experiment, experiment_plugin)
```

@@

```{julia}
paths = [Experiments.load_path(joinpath(output_path, string(keys(generators)[j]))) for j ∈ 1:length(generators)]
```

```{julia}
function plot_state(path, t; γ=0.75, μ = 0.05, k = 1, length_out=500, size=(150,150), title="")
    chosen = map(p -> p.γ == γ && p.μ == μ && p.t==t && p.k==k, path)
    path = path[chosen][1]
    X = path.X̲'
    y = vec(path.y̲')
    plt = plot_contour(X,y,path.𝑴,length_out=length_out,colorbar=cb,title=title)
    plt = plot(plt, axis=nothing, size=size, legend=false)
end
plot_state(paths[2], 1)
```

```{julia}
#| eval: false
using Main.Experiments: plot_path
paths = [Experiments.load_path(joinpath(output_path, string(keys(generators)[j]))) for j ∈ 1:length(generators)]
anim = Experiments.plot_path(paths[1],Γ=γ,𝙈=μ)
gif(anim,joinpath(www_path,"bayesian.gif"), fps=2)
anim = Experiments.plot_path(paths[2],Γ=γ,𝙈=μ)
gif(anim,joinpath(www_path,"plugin.gif"), fps=2)
```

@@

  while epoch <= epochs && !stopping_criterium_reached
    for d in data
      gs = gradient(Flux.Flux.params(nn)) do
        l = loss(d...)
      end
      update!(opt, Flux.Flux.params(nn), gs)
    end
    avg_l = vcat(avg_l,avg_loss(data))
    plot!(p1, [0:epoch], avg_l, color=1)
    scatter!(p1, [0:epoch], avg_l, color=1)
    acc = vcat(acc,accuracy(data))
    plot!(p2, [0:epoch], acc, color=1)
    scatter!(p2, [0:epoch], acc, color=1)
    plt=plot(p1,p2, size=(600,300))
    frame(anim, plt)

@@

```{julia}
# Experiments:
experiment = Experiments.Experiment(X',y',models[:Plugin],target,grid_,n_rounds)
experiment_plugin = Experiments.Experiment(X',y',models[:Plugin],target,grid_,n_rounds)
experiments = (experiment, experiment_plugin);
```
